Assessing landscape N removal in coastal New England catchments using the N-Sink

### 2023-06-05 manuscript/manuscript.Rmd
Change Fig 4 coding to use ggplot() and spatraster

niantic_fp_b <- nsink_generate_flowpath(start_loc_inter_b, niantic_data)
niantic_fp_removal_b <- nsink_summarize_flowpath(niantic_fp_b, niantic_removal)
raster::plot(niantic_static_maps$transport_idx, breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100), 
             col = c("#38A1D0", "#7AB4C0", "#A2C8B0","#C3DC9D", "#E2F088", "#F5E871",
                     "#F9C159", "#F99844", "#F56A2E","#EF2820"))
huc <- niantic_data$huc
streams <- st_intersection(huc, niantic_data$streams)
plot(streams, add = TRUE, col = "dodgerblue")
plot(niantic_data$lakes, add = TRUE, col = "dodgerblue", border = "dodgerblue")
plot(st_geometry(niantic_fp_a$flowpath_network), add = TRUE, col = "gray40", lwd = 3.0)
plot(st_geometry(niantic_fp_a$flowpath_ends), add = TRUE, col = "gray40", lwd = 3.0)
plot(st_geometry(niantic_fp_b$flowpath_network), add = TRUE, col = "gray0", lwd = 2.0, lty = 2)
plot(st_geometry(niantic_fp_b$flowpath_ends), add = TRUE, col = "gray0", lwd = 2.0, lty = 2)
x <- c(pta[1], ptb[1])
y <- c(pta[2], ptb[2])
ab <- st_multipoint(matrix(c(x,y), nrow = 2, ncol = 2))
ab_plot <- st_sf(st_sfc(ab), crs = aea)
plot(ab_plot, add = TRUE, pch = 16)
text(ab, labels = c("A", "B"), pos = 1, offset = 0.4)
```

>>>>

niantic_fp_b <- nsink_generate_flowpath(start_loc_inter_b, niantic_data)
niantic_fp_removal_b <- nsink_summarize_flowpath(niantic_fp_b, niantic_removal)
raster::plot(niantic_static_maps$transport_idx, breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100), 
             col = c("#38A1D0", "#7AB4C0", "#A2C8B0","#C3DC9D", "#E2F088", "#F5E871",
                     "#F9C159", "#F99844", "#F56A2E","#EF2820"))
huc <- niantic_data$huc
streams <- st_intersection(huc, niantic_data$streams)
x <- c(pta[1], ptb[1])
y <- c(pta[2], ptb[2])
ab <- st_multipoint(matrix(c(x,y), nrow = 2, ncol = 2))
ab_plot <- st_sf(st_sfc(ab), crs = aea)
plot(ab_plot, add = TRUE, pch = 16)
text(ab, labels = c("A", "B"), pos = 1, offset = 0.4)
from <- c(seq(0,90,10), NA)
to <- c(seq(10,100,10), NA)
#matrix(c(from,to,to),ncol = 3)
tnsport_idx <- classify(rast(niantic_static_maps$transport_idx),matrix(c(from,to,to),ncol = 3))
values(tnsport_idx) <- factor(values(tnsport_idx))
ggplot() +
  geom_spatraster(data = tnsport_idx) +
  scale_fill_manual(values = c("#38A1D0", "#7AB4C0", "#A2C8B0","#C3DC9D", 
                                        "#E2F088", "#F5E871", "#F9C159", 
                                        "#F99844", "#F56A2E","#EF2820"), 
                                        na.value = NA, na.translate = FALSE) +
  geom_sf(data = streams, color = "dodgerblue", linewidth = 0.7) +
  geom_sf(data = niantic_data$lakes, fill = "dodgerblue", color = "dodgerblue") +
  geom_sf(data = niantic_fp_a$flowpath_network, color = "grey40", linewidth = 2.5) +
  geom_sf(data = niantic_fp_a$flowpath_ends, color = "grey40", linewidth = 2.5) +
  geom_sf(data = niantic_fp_b$flowpath_network, color = "grey0", linewidth = 0.9) +
  geom_sf(data = niantic_fp_b$flowpath_ends, color = "grey0", linewidth = 0.9) +
  geom_sf(data = ab_plot, pch = 16, size = 2) + 
  geom_sf_label(data = ab_plot, aes(label = labels))
```
